Tropical mathematics and the Lambda-calculus I

### 2023-07-29 CSL24/sectionTaylip.tex
commit

\begin{corollary}
Suppose $x: A \vdash_{\STLC}M:B$ and $\vdash_{\STLC} N:A$. 
Then for all $t\in \Te{M}$, with $t\neq \infty$, and $\delta>0$, the tLs $\model{ x:A\vdash_{\STLC}M:B}^{!}$ is $\frac{\model{t}(\model{N}+2\delta)}{\delta}$-Lipschitz over the open ball
 $B_{\delta}(\model{N})$.
\end{corollary}
{\color{red}ADD PROOF SKETCH}

>>>>

\begin{corollary}
Suppose $x: A \vdash_{\STLC}M:B$ and $\vdash_{\STLC} N:A$. 
Then for all $t\in \Te{M}$ such that $\model{t}^{!}(\model{N})\neq \infty$, and $\delta>0$, the tLs $\model{ x:A\vdash_{\STLC}M:B}^{!}$ is $\frac{\model{t}^{!}(\model{N}+2\delta)}{\delta}$-Lipschitz over the open ball
 $B_{\delta}(\model{N})$.
\end{corollary}
{\color{red}ADD PROOF SKETCH}
